Working document to try to explain why/how ATAs influence coexistence in an intuitive way for referee 3

### 2023-07-12 paper/ExplanationOfATAEffectsWorkingDoc.tex
adding stuff before lunch

>>>>

The storage effect stably contributes to coexistence through 
temporal niche partitioning with EC covariance and buffered population growth.
Under invader-resident analysis [rare-common], EC covariance limits the resident by 
coupling high environmental responses with high intraspecific competition. The magnitude
of the storage effects then depends on the EC covariance of the invader. Because the 
invader is introduced into the resident steady state community at close to zero density, 
its C is only a result of interspecific competition from the resident. Thus, the more closely 
related the invader's EC relationship is, the more interspecific competition it experiences, 
destabalizing coexistence. Equivalently, invader EC relationships with more spread stably
contribute to coexistence (through the storage effect). As seen in Fig. \ref{thefig}, ATAs in the invader EC relationship changes its bivariate distribution to both have more spread about the "central line" and be more densely situated about the "central line".
